Proposed Solution

### 2017-01-23 CAV17/secs/motiv.tex
clarify motiv

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    MISSING ENTRY ERROR: Expected "extension=pgsal.so"
    in the same file: "extension=curl.so"
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    key_buffer_size = 384M
    max_heap_table_size = 128M
    max_connections = 8
    thread_cache_size = 8
        ...
    sort_buffer_size = 32M
    join_buffer_size = 32M
    read_buffer_size = 32M
    read_rnd_buffer_size = 8M
        ...
\end{lstlisting}

>>>>

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    MISSING ENTRY ERROR: Expected "extension=pgsal.so"
    in the same file: "extension=curl.so"
    w/ confidence ...
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
  max_connections               = 64
  thread_cache_size             = 8
  thread_concurrency            = 8

  key_buffer_size               = 4G
  max_heap_table_size           = 128M

  join_buffer_size              = 32M
  sort_buffer_size              = 32M    
\end{lstlisting}
